My title

### 2022-03-16 outputs/paper/paper.Rmd
finished add to intro and data sections

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

Possible Research Questions:

General Family

- What do families in Canada look like? (in terms of marriage status, number of children, ethnic diversity and immigration and income, etc.)?
- How does this differ by province/geographical region?

Marriage & relationships

- Do couples prefer marriage over common-law relationships? Is this related in any way to religious affiliation?
- Do couples want to have children?
- What is the rate of separation/divorce?

@@

Some variables have several missing values.

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: https://github.com/jmacattack27/General-Social-Survey-on-Family-2017- ."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

In this paper, we show a snapshot of what Canadian families look like using data from the 2017 General Social Survey on Family. Specifically, we address the following research questions:

- What are the most common family sizes and types (e.g. married couple, single-parent, etc.)?
- Do most Canadians get married and how many children do they have?
- What is distribution of education level of Canadians?
- Are Canadian households mainly low-income, middle-income or high-income?
- Which provinces have the most immigrant families?
- Is religion important in Canadian families?
- What is the mental health of Canadians like, and what factors may be related to this?

@@

Strengths include that there is a large number of variables so there is a lot of opportunity for data exploration and research insights, and there is also a large number of observations for us to draw meaningful conclusions. A weakness includes that response categories for some of the questionnaire questions were collapsed in the code variables provided, for example mother tongue only lists English, French and non-official languages, and race of respondent became visible minority (yes/no), so we cannot comment on the full range of diverse responses.
